A Classical Density-Functional Theory for Describing Water Interfaces

### 2010-12-14 paper/paper.tex
Fix bug in a2 from comparison with Jackson.
Tested-on: collins (Linux 2.6.32-5-amd64)
Clean up code in SAFT.
Tested-on: collins (Linux 2.6.32-5-amd64)

\begin{figure}
\begin{center}
%\includegraphics[width=\columnwidth]{free-energy/free-energy}
\end{center}
\caption{By plotting the free energy vs. density it is possible to
  determine a liquid or vapor state by the energy minima.  We can adjust the
  available free parameters to ensure that liquid and vapor coexist with
  the same minimum free energy.  }
\label{fig:homogeneous}
\end{figure}

@@

>>>>

@@

In order to ensure that the empirical parameters are correct, we test
the vapor pressure (see Figure~\ref{fig:equation-of-state}) and
saturated liquid density (see
Figure~\ref{fig:saturated-liquid-density}) against experimental
values.  To find these densities, we use the ``common tangent'' rule,
as illustrated in Figure~\ref{fig:homogeneous}.
\begin{figure}
\begin{center}
\includegraphics[width=\columnwidth]{figs/finding-vapor-pressure}
\end{center}
\caption{By plotting the free energy vs. density it is possible to
  determine a saturated liquid or vapor state by the common tangent
  method.  }
\label{fig:homogeneous}
\end{figure}
